### 2015-02-28 icfp15-servo/rust.tex
Add section on Rust traits

\begin{figure}
\begin{lstlisting}
fn main() {
  // An immutable borrowed pointer to a
  // stack-allocated integer
  let data = &1;

@@

>>>>

\begin{figure}
\begin{lstlisting}
fn main() {
  // An immutably borrowed pointer to a
  // stack-allocated integer
  let data = &1;

@@

\subsection{Traits and polymorphism}

Rust supports both static and dynamic parametric polymorphism via \emph{traits},
which build on ideas from type classes and type families in Haskell~\cite{haskell}.

As with Haskell type classes, traits define functions and types that are associated
with all implementing types. Function and types in turn can be parameterized over
generic types that are bounded by traits, as with the trait that defines overloaded
addition in \figref{fig:fn-trait}

Such calls to associated functions are statically dispatched, so optimize well,
but Rust also allows types that implement traits to be packaged with a vtable
so that functions can be resolved dynamically. Because Rust's generics must
perform as well as C++'s inlined templates, performance-sensitive Rust
code tends to prefer the static dispatch of traits-as-typeclasses.
This is true of much of the standard library.

Rust includes several types of closures that are distinguished by whether
they own or borrow their environment, and these are defined as traits.

\begin{figure}
\begin{lstlisting}
pub trait Add<RHS=Self> {
  type Output;

  fn add(self, rhs: RHS) -> Self::Output;
}

fn add_pair<T>(pair: (T, T)) -> T::Output
                             where T: Add {
  pair.0 + pair.1
}
\end{lstlisting}
  \caption{Rust trait with associated type.}
  \label{fig:fn-trait}
\end{figure}
